Towards a reproducible framework for undergraduate data science research

### 2019-12-03 Rmd/methods.Rmd
updated methods

@@

The brainstorming sessions thus led to one set of questions for each student.

>>>>

We also incorporated data availability into our question formulation. We limited questions to those 
that could be studied with publicly available data. This practice also enabled reproducibility of
our analyses, since students could share the URL from which they accessed data.

After identifying research questions and publicly available data, 
the next step is to decide on informative data visualizations and quantitative analyses. Because 
both projects primarily involved exploratory analyses of times series, 
we encouraged students to think about
visualizations that might reveal relationships over time.

### Examples

@@
